### 2017-05-19 sheets/basis-3/sheet-basis-3.tex
Fixed the diagram of 3.4 to match the orientation of n.t. diagrams in Leinster.

\begin{exercise}
  For a fixed set $A$, the map taking $B$ to $B^A \times A$ can be extended to
  a functor $F_A:\mathbf{Set} \to \mathbf{Set}$ as follows:
  \begin{align*}
    F_A(B) & =  B^A \times A\\
    F_A(f: B \to C) & =  (F \circ \_) \times id_A
  \end{align*}
  The fact that $eval: F_A \to I_{\mathbf{Set}}$ is a natural transformation follows from the commutativity of the diagram
\[
  \begin{tikzcd}
    F_A(C) = C^A \times A \arrow{rrr}{eval_{AC}} \arrow{dd}{F_A(g)=(g\circ \_) \times id_A} & & & C = I_{\mathbf{Set}}(C) \arrow{dd}{g = I_{\mathbf{Set}(g)}} \\
                                                                                           & & & \\
    F_A(B) = B^A \times A \arrow{rrr}{eval_{AB}} & & & B = I_{\mathbf{Set}}(B)
  \end{tikzcd}
\]
for each $g: C \to B$.

>>>>

\begin{definition}{Product of Morphisms inside a Category}
  Let $\cat{A}$ be a category and $A, B, C, D \in \ob(\cat{A})$ with $f \from A \to C$ and $g \from B \to D$.
  The product morphism of $f$ and $g$, written $f \times g$, is a function
  \begin{align*}
    A \times B &\qquad\to\qquad C \times D\\
    (a, b) &\qquad\mapsto\qquad (f(a), g(b))
  \end{align*}
\end{definition}

\newcommand{\eval}[1]{\ensuremath{\mathsf{eval}^{#1}\xspace}}

\begin{exercise}
  For a fixed set $A$, the map taking $B$ to $B^A \times A$ can be extended to
  a functor $F_A:\mathbf{Set} \to \mathbf{Set}$ as follows:
  \begin{align*}
    F_A(B) & =  B^A \times A\\
    F_A(f: B \to C) & =  (f \circ \_) \times 1_A
  \end{align*}
  The function $\eval{A} \from F_A \to 1_{\mathbf{Set}}$, defined as $\eval{A}(f,a) := f(a)$, is a natural transformation if the following diagram commutes for each $g \from B \to C$.
\[
  \begin{tikzcd}
    F_A(B) = B^A \times A \arrow{rrr}{F_A(g)=(g\circ \_) \times 1_A} \arrow{dd}[swap]{\eval{A}_B} & & & 1_{\mathbf{Set}}(B) = B \arrow{dd}{\eval{A}_C} \\
                                                                                           & & & \\
    F_A(C) = C^A \times A \arrow{rrr}[swap]{1_{\mathbf{Set}}(g) = g} & & & 1_{\mathbf{Set}}(C) = C
  \end{tikzcd}
\]
